### 2018-03-22 Sections/cryptowars.tex
minor

Classical public- and private-key encryption protocols are typically based upon the assumption of computational security (e.g the computational complexity of performing integer factorisation in the case of RSA public-key encryption, or solving a complex satisfiability problem in the case of private-key encryption), whereas quantum encryption protocols are typically information theoretically secure (e.g the one-time-pad using QKD).

@@

Importantly, the secrecy of the one-time-pad\index{One-time pad cipher} strictly requires that a key never be reused. A fresh key must be generated for each message sent, otherwise trivial frequency analysis\index{Frequency analysis} techniques can be employed to compromise security. If the same key $k$ is used to encode two messages $s_1$ and $s_2$, yielding ciphertexts,
\begin{align}
c_1&=s_1\oplus k,\nonumber\\
c_2&=s_2\oplus k,
\end{align}
then we trivially obtain,
\begin{align}
c_1 \oplus c_2 &= (s_1 \oplus k) \oplus (s_2 \oplus k) \nonumber \\
&= (s_1 \oplus s_2) \oplus (k \oplus k) \nonumber \\
&= s_1 \oplus s_2,
\end{align}
which is independent of the key. Now a frequency analysis on the bitwise XOR of two plaintexts can be applied, without requiring any knowledge of the key whatsoever.

@@

Although during the Cold War Soviet diplomats would literally carry briefcases between countries full of paper with random data for use in a one-time-pad, it is clearly not suitable for everyday applications!

@@

Hash functions have broad applicability throughout computer science, but here we are most interested in \textit{cryptographic hash functions} for use in cryptography, which impose strong conditions on the difficulty of inversion and their quasi-random characteristics.

The standard cryptographic hash function with mainstream adoption is the 256-bit Secure Hashing Algorithm (SHA256\index{SHA256}), which generates 256-bit hashes.

@@

Quantum key distribution (QKD) protocols facilitate shared, secret randomness, where any intercept-resend\index{Intercept-resend attack} (or man-in-the-middle attack) attack may be detected and rejected, guaranteed by the laws of quantum physics (specifically the Heisenberg uncertainty principle\index{Heisenberg uncertainty principle} and no-cloning theorem\index{No-cloning theorem}). This shared, secret randomness may subsequently be employed in a one-time-pad cipher\index{One-time-pad cipher}, presenting us with true information-theoretic security\index{Information-theoretic security}.

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function BB84():
\begin{enumerate}
\item Alice chooses a random bit, $0$ or $1$.
\item Alice randomly chooses a basis, $\hat{X}$ or $\hat{Z}$.
\item Depending on the choice of basis, she encodes her bit into the polarisation of a single photon as:
\begin{align}
\ket{0}_Z &\equiv \ket{H}, \nonumber \\
\ket{1}_Z &\equiv \ket{V},
\end{align}
or,
\begin{align}
\ket{0}_X &\equiv \frac{1}{\sqrt{2}}(\ket{H}+\ket{V}), \nonumber \\
\ket{1}_X &\equiv \frac{1}{\sqrt{2}}(\ket{H}-\ket{V}).
\end{align}
\item Encoding into the randomly chosen basis, she transmits the randomly chosen bit to Bob.
\item She does not announce the choice of bit or basis.
\item Bob measures the bit in a randomly chosen basis, $\hat{X}$ or $\hat{Z}$.
\item The above is repeated many times.
\item Upon receipt of all qubits, Alice (publicly) announces the basis used for encoding each bit sent.
\item Qubits where Bob measured in the opposite basis to which Alice encoded are discarded, as they will be decorrelated from Alice.
\item The remaining measurement outcomes are guaranteed to yield identical bits between Alice and Bob.
\item Remaining is roughly half as many bits as were sent, which are random, but guaranteed to be identical between Alice and Bob.
\item Alice and Bob sacrifice some of their bits by publicly communicating them to check for consistency. This rules out intercept-resend attacks.
\item Privacy amplification may be used to distill the partially compromised key into a shorter but more secret one.
\end{enumerate}}}}
\caption{BB84\index{BB84 protocol} QKD protocol using polarisation-encoded\index{Polarisation encoding} photons. Upon completion of the protocol, Alice and Bob share a random bit-string for use in a one-time-pad cipher\index{One-time pad cipher}.}\label{alg:bb84}
\end{table}

@@

To understand the secrecy of the protocol as described in Alg.~\ref{alg:bb84}, suppose an eavesdropper, Eve, were to perform an intercept-resend\index{Intercept-resend attack} attack on the channel between Alice and Bob. At that stage in the protocol Alice had not yet announced her choice of encoding bases, and Eve will not know the bases in which to measure states without randomly collapsing them onto values inconsistent with Alice's encoding. Thus, by sacrificing some of their shared bits, via openly communicating them to one another for comparison, such an attack will be detected with asymptotically high security. Now Alice and Bob have great confidence that they have a shared, secret, random bit-string, which may subsequently be employed in a one-time-pad\index{One-time-pad protocol} with perfect secrecy.

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function E91():
\begin{enumerate}
\item A central server shares a Bell-pair between Alice and Bob,
\begin{align}
\ket{\Phi^+} = \frac{1}{\sqrt{2}}(\ket{0}_A\ket{0}_B+\ket{1}_A\ket{1}_B).
\end{align}
\item Alice randomly measures her qubit in either the $\hat{X}$ or $\hat{Z}$ basis.
\item Bob randomly measures his qubit in either the $\hat{X}$ or $\hat{Z}$ basis.
\item Alice and Bob share what their measurement bases were (classically and unencrypted).
\item When Alice and Bob's bases were consistent they store the measurement outcomes as a shared random bit.
\item Alice and Bob sacrifice some of their bits by publicly communicating them to check for consistency. This rules out intercept-resend attacks.
\item Privacy amplification may be used to distill the partially compromised key into a shorter but more secret one.
\end{enumerate}}}}
\caption{E91\index{E91 protocol} QKD protocol using polarisation-encoded\index{Polarisation encoding} photonic Bell-pairs. Upon completion of the protocol, Alice and Bob share a random bit-string of ruse in a one-time-pad cipher\index{One-time pad cipher}.}\label{alg:e91}
\end{table}

@@

In the near future, as QKD schemes begin their rollout in space and on Earth, random bits from the QKD implementation will be very expensive and exhibit low bandwidth. Suppose we wanted to securely videoconference across the globe. For just a single user this would require megabits per second of shared random bits, which will quickly saturate the capacity of overhead quantum satellites. Instead, let us use the QKD system to securely share just a 256-bit private session key\index{Session key} between two users. This is subsequently employed for AES256 encryption that operates entirely over the classical network, which we regard as extremely cheap. Importantly, unlike one-time-pad implementations, this session key may be reused. Now we have a hybrid system which is not quantum-compromised, but which overcomes the cost and bandwidth issues associated with upcoming QKD networks.

>>>>

Classical public- and private-key encryption protocols are typically based upon the assumption of computational security (e.g the computational complexity of performing integer factorisation in the case of RSA public-key encryption, or solving a complex satisfiability problem in the case of private-key encryption), whereas quantum encryption protocols are typically information theoretically secure (e.g the one-time pad using QKD).

@@

Importantly, the secrecy of the one-time pad\index{One-time pad cipher} strictly requires that a key never be reused. A fresh key must be generated for each message sent, otherwise trivial frequency analysis\index{Frequency analysis} techniques can be employed to compromise security. If the same key $k$ is used to encode two messages $s_1$ and $s_2$, yielding ciphertexts,
\begin{align}
c_1&=s_1\oplus k,\nonumber\\
c_2&=s_2\oplus k,
\end{align}
then we trivially obtain,
\begin{align}
c_1 \oplus c_2 &= (s_1 \oplus k) \oplus (s_2 \oplus k) \nonumber \\
&= (s_1 \oplus s_2) \oplus (k \oplus k) \nonumber \\
&= s_1 \oplus s_2,
\end{align}
which is independent of the key. Now a frequency analysis on the bitwise XOR of two plaintexts can be applied, without requiring any knowledge of the key whatsoever.

@@

Although during the Cold War Soviet diplomats would literally carry briefcases between countries full of paper with random data for use in a one-time pad, it is clearly not suitable for everyday applications!

@@

Hash functions have broad applicability throughout computer science, but here we are most interested in \textit{cryptographic hash functions} for use in cryptography, which impose strong conditions on the difficulty of inversion and their quasi-random characteristics. Most notably, changing a single bit in the input string ought to flip approximately half the bits of the hash on average.

The standard cryptographic hash function with mainstream adoption is the 256-bit Secure Hashing Algorithm (SHA256\index{SHA256}), which generates 256-bit hashes. The algorithm is extremely efficient to implement digitally, and exhibits $O(n)$ runtime for input string length $n$.

@@

Quantum key distribution (QKD) protocols facilitate shared, secret randomness, where any intercept-resend\index{Intercept-resend attack} (or man-in-the-middle attack) attack may be detected and rejected, guaranteed by the laws of quantum physics (specifically the Heisenberg uncertainty principle\index{Heisenberg uncertainty principle} and no-cloning theorem\index{No-cloning theorem}). This shared, secret randomness may subsequently be employed in a one-time pad cipher\index{One-time pad cipher}, presenting us with true information-theoretic security\index{Information-theoretic security}.

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function BB84():
\begin{enumerate}
\item Alice chooses a random bit, $0$ or $1$.
\item Alice randomly chooses a basis, $\hat{X}$ or $\hat{Z}$.
\item Depending on the choice of basis, she encodes her bit into the polarisation of a single photon as:
\begin{align}
\ket{0}_Z &\equiv \ket{H}, \nonumber \\
\ket{1}_Z &\equiv \ket{V},
\end{align}
or,
\begin{align}
\ket{0}_X &\equiv \frac{1}{\sqrt{2}}(\ket{H}+\ket{V}), \nonumber \\
\ket{1}_X &\equiv \frac{1}{\sqrt{2}}(\ket{H}-\ket{V}).
\end{align}
\item Encoding into the randomly chosen basis, she transmits the randomly chosen bit to Bob.
\item She does not announce the choice of bit or basis.
\item Bob measures the bit in a randomly chosen basis, $\hat{X}$ or $\hat{Z}$.
\item The above is repeated many times.
\item Upon receipt of all qubits, Alice (publicly) announces the basis used for encoding each bit sent.
\item Qubits where Bob measured in the opposite basis to which Alice encoded are discarded, as they will be decorrelated from Alice.
\item The remaining measurement outcomes are guaranteed to yield identical bits between Alice and Bob.
\item Remaining is roughly half as many bits as were sent, which are random, but guaranteed to be identical between Alice and Bob.
\item Alice and Bob sacrifice some of their bits by publicly communicating them to check for consistency. This rules out intercept-resend attacks.
\item Privacy amplification may be used to distill the partially compromised key into a shorter but more secret one.
\end{enumerate}}}}
\caption{BB84\index{BB84 protocol} QKD protocol using polarisation-encoded\index{Polarisation encoding} photons. Upon completion of the protocol, Alice and Bob share a random bit-string for use in a one-time pad cipher\index{One-time pad cipher}.}\label{alg:bb84}
\end{table}

@@

To understand the secrecy of the protocol as described in Alg.~\ref{alg:bb84}, suppose an eavesdropper, Eve, were to perform an intercept-resend\index{Intercept-resend attack} attack on the channel between Alice and Bob. At that stage in the protocol Alice had not yet announced her choice of encoding bases, and Eve will not know the bases in which to measure states without randomly collapsing them onto values inconsistent with Alice's encoding. Thus, by sacrificing some of their shared bits, via openly communicating them to one another for comparison, such an attack will be detected with asymptotically high security. Now Alice and Bob have great confidence that they have a shared, secret, random bit-string, which may subsequently be employed in a one-time pad\index{One-time pad cipher} with perfect secrecy.

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function E91():
\begin{enumerate}
\item A central server shares a Bell-pair between Alice and Bob,
\begin{align}
\ket{\Phi^+} = \frac{1}{\sqrt{2}}(\ket{0}_A\ket{0}_B+\ket{1}_A\ket{1}_B).
\end{align}
\item Alice randomly measures her qubit in either the $\hat{X}$ or $\hat{Z}$ basis.
\item Bob randomly measures his qubit in either the $\hat{X}$ or $\hat{Z}$ basis.
\item Alice and Bob share what their measurement bases were (classically and unencrypted).
\item When Alice and Bob's bases were consistent they store the measurement outcomes as a shared random bit.
\item Alice and Bob sacrifice some of their bits by publicly communicating them to check for consistency. This rules out intercept-resend attacks.
\item Privacy amplification may be used to distill the partially compromised key into a shorter but more secret one.
\end{enumerate}}}}
\caption{E91\index{E91 protocol} QKD protocol using polarisation-encoded\index{Polarisation encoding} photonic Bell-pairs. Upon completion of the protocol, Alice and Bob share a random bit-string of ruse in a one-time pad cipher\index{One-time pad cipher}.}\label{alg:e91}
\end{table}

@@

In the near future, as QKD schemes begin their rollout in space and on Earth, random bits from the QKD implementation will be very expensive and exhibit low bandwidth. Suppose we wanted to securely videoconference across the globe. For just a single user this would require megabits per second of shared random bits, which will quickly saturate the capacity of overhead quantum satellites. Instead, let us use the QKD system to securely share just a 256-bit private session key\index{Session key} between two users. This is subsequently employed for AES256 encryption that operates entirely over the classical network, which we regard as extremely cheap. Importantly, unlike one-time pad implementations, this session key may be reused. Now we have a hybrid system which is not quantum-compromised, but which overcomes the cost and bandwidth issues associated with upcoming QKD networks.

### 2018-03-22 Sections/interconnecting_and_interfacing_quantum_networks.tex
Crypto, CV
minor

In addition to single atoms with well-defined electronic structure, atomic ensembles \cite{DLCZ, bib:Chou05} can be used, whereby the absorption of a photon creates a \textit{collective excitation}\index{Collective excitations} -- a superposition of a single excitation across all the atoms in the ensemble. Specifically, excitations are represented using collective excitation operators,
\begin{align}\index{Collective excitations}
\hat{S}^\dag = \frac{1}{\sqrt{N}}\sum_{i=1}^N \hat{S}_i^\dag,
\end{align}
where,
\begin{align}
\hat{S}_i^\dag=\ket{e}_i\bra{g}_i,
\end{align}
is the excitation operator for the $i$th atom in the ensemble, $\ket{g}_i$ and $\ket{e}_i$ are the ground and excited states for the $i$th particle, and there are $N$ atoms. The state of a single collective excitation is then given by,
\begin{align}
\ket{\psi_\text{collective}} = \hat{S}^\dag \ket{g}^{\otimes N}.	
\end{align}

Atomic ensembles are essentially well-engineered clouds of atomic gasses, trapped in a glass container, coupled to an optical mode. Atomic ensembles have been demonstrated with extremely long coherence lifetimes ($\tau_2\approx$100ms \comment{Check this!}), operating at room temperatures (a very attractive feature on its own). They exhibit \textit{collective enhancement}\index{Collective enhancement} in their coupling to the optical mode -- the optical coupling strength is amplified by a factor quadratic in $N$ compared to single-atom optical coupling, mitigating the need for a cavity.

>>>>

In addition to single atoms with well-defined electronic structure, atomic ensembles \cite{DLCZ, bib:Chou05} can be used, whereby the absorption of a photon creates a \textit{collective excitation}\index{Collective excitations} -- a superposition of a single excitation across all the atoms in the ensemble. Specifically, excitations are represented using collective excitation operators,
\begin{align}\index{Collective excitation operator}
\hat{S}^\dag = \frac{1}{\sqrt{N}}\sum_{i=1}^N \hat{S}_i^\dag,
\end{align}
where,
\begin{align}
\hat{S}_i^\dag=\ket{e}_i\bra{g}_i,
\end{align}
is the excitation operator for the $i$th atom in the ensemble, $\ket{g}_i$ and $\ket{e}_i$ are the ground and excited states for the $i$th particle, and there are $N$ atoms. The state of a single collective excitation is then given by,
\begin{align}
\ket{\psi_\text{collective}} = \hat{S}^\dag \ket{g}^{\otimes N}.	
\end{align}

Atomic ensembles are essentially well-engineered clouds of atomic gasses, trapped in a glass container, coupled to an optical mode. Atomic ensembles have been demonstrated with extremely long coherence lifetimes ($\tau_2\approx$100ms \comment{Check this!}\index{$\tau_2$ time}), operating at room temperatures (a very attractive feature on its own). They exhibit \textit{collective enhancement}\index{Collective enhancement} in their coupling to the optical mode -- the optical coupling strength is amplified by a factor quadratic in $N$ compared to single-atom optical coupling, mitigating the need for a cavity.
